A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-09 paper/main.tex
paper: fix Judith's attribution

We are grateful to prof.~McKay for discussing
the feasibility of certain graph restrictions and
to Judith van Stegeren\footnote{\url{http://jd7h.com/}}
for drawing the figures in this paper.

>>>>

We are grateful to prof.~McKay for discussing
the feasibility of certain graph restrictions and
to Judith van Stegeren\footnote{\url{http://jd7h.com/}}
for drawing the first two figures in this paper.
